---
title: "Shiny App for Country Maps and Flags"
author: "Vitor Dantas"
date: "7/23/2019"
output: ioslides_presentation
---

## Country Maps and Flags!

This Shiny app written in R and hosted at shinyapps.io lets you choose
a country to:

- See where it is located in the world
- Check out the looks of its flag!
- Browse the interactive map

## Under the hood

A simple app, but powerful because it stands on the shoulders of libraries:

- Shiny
- Leaflet
- jsonlite
- The REST Countries API

## Sample results (1/2)

```{r echo=FALSE,message=FALSE}
library(dplyr)
library(jsonlite)
library(leaflet)
```

```{r echo=FALSE,cache=TRUE}
jsonCountryData <- fromJSON("https://restcountries.eu/rest/v2/all")
```

```{r echo=FALSE}
countryData <- jsonCountryData %>%
    filter(sapply(jsonCountryData$latlng, length) == 2) %>%
    transmute(name,
              alpha2Code,
              flag,
              lat = sapply(latlng, "[[", 1),
              lng = sapply(latlng, "[[", 2))
```

For a little demonstration, here is the expected result result when you select "Brazil"!

```{r echo=FALSE,message=FALSE,fig.width=6,fig.height=3}
selectedCountryRow <- countryData[countryData$name == "Brazil", ]

countryData %>%
    leaflet() %>%
    addTiles() %>%
    addMarkers(icon = makeIcon(iconUrl = countryData$flag,
                               iconWidth = 40,
                               iconHeight = 20),
               clusterOptions = markerClusterOptions(maxClusterRadius = 40,
                                                     showCoverageOnHover = FALSE)) %>%
    setView(lng = selectedCountryRow$lng,
                    lat = selectedCountryRow$lat,
                    zoom = 4)
```

## Sample results (2/2)

And that's what you get if you select "India".

```{r echo=FALSE,message=FALSE,fig.width=6,fig.height=3}
selectedCountryRow <- countryData[countryData$name == "India", ]

countryData %>%
    leaflet() %>%
    addTiles() %>%
    addMarkers(icon = makeIcon(iconUrl = countryData$flag,
                               iconWidth = 40,
                               iconHeight = 20),
               clusterOptions = markerClusterOptions(maxClusterRadius = 40,
                                                     showCoverageOnHover = FALSE)) %>%
    setView(lng = selectedCountryRow$lng,
                    lat = selectedCountryRow$lat,
                    zoom = 4)
```

Enjoy the app!

https://vitorcd.shinyapps.io/developing-data-products-course-project/